Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-19 Document/paper.tex
edit

\cite{Debattista08} reported a similar twisting effect, but only at radii smaller
than the disk radius. 
At radii larger than the disk radius, they find, the dark matter
shells stop twisting. 
\cite{JingSuto02} also reported shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they the twisting as an artifact resulting from high values of the
$c/b$ ratios that make the determination of the medium axis boisy.
Could then high triaxility values explain the twisting as a result of
erratic axis directions? 
If the triaxiality were the main culprit behind the twisting, the
correlation between the two quantities should be constant at every
radii.
In Figure \ref{fig:alignment_correlations} we already showed that this
correlation strongly depends on radius, we conclude that high
triaxiality values cannot be the full explanation.
Furthermore the twisting happens in such a way that it allows and
almost perfect alignment between the stellar disk at $0.1R{200}$ and
the halo shape measured at $0.25R_{200}$

>>>>

\cite{Debattista08} reported a similar twisting effect, but only at radii smaller
than the disk radius. 
At radii larger than the disk radius, they find, the dark matter
shells stop twisting. 
\cite{JingSuto02} also reported shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they the twisting as an artifact resulting from high values of the
$c/b$ ratios that make the determination of the medium axis boisy.
Could then high triaxility values explain the twisting as a result of
erratic axis directions? 
If the triaxiality were the main culprit behind the twisting, the
correlation between the two quantities should be constant at every
radii.
In Figure \ref{fig:alignment_correlations} we already showed that this
correlation strongly depends on radius, we conclude that high
triaxiality values cannot be the full explanation.
Furthermore the twisting happens in such a way that it allows an
almost perfect alignment between the stellar disk at $0.1R{200}$ and
the halo shape measured at $0.25R_{200}$
